Fractional Types

### 2016-12-18 typespp.tex
more comments in 4.2

The first step is to enrich the types to pointed types $\mathbb{T_\bullet}$
where each type $\mathbb{T}$ refers to a particular value $v$ in
$\mathbb{T}$. We then allow universal quantification over indices $k$
associated to values, over a collection of types.
In particular, the type
$\forall k.[\order{c} \circledast \iorder{c}, \langle c^k, 1/c^k \rangle]$
imposes a constraint on the two values associated with the types $\order{c}$ and
$\iorder{c}$; they must be ``synchronized'' by sharing the same $k$. In
general, a pointed type will be of the form
$\forall\overline{k}.[\mathbb{T},v]$ for some sequence of integers
$\overline{k}$ and some value $v$ in $\mathbb{T}$, which might of course refer
to the integers of $\overline{k}$ to enforce some synchronization among its
sub-values.  It is good to remember that there is no loss in generality
in going to pointed types, as all fractional types are inhabited (see
remark in Sec.~\ref{sec:symmetryg}.

>>>>

The first step is to enrich the types to pointed types $\mathbb{T_\bullet}$
where each type $\mathbb{T}$ refers to a particular value $v$ in
$\mathbb{T}$. We then allow universal quantification over indices $k$
associated to values, over a collection of types.
In particular, the type
$\forall k.[\order{c} \circledast \iorder{c}, \langle c^k, 1/c^k \rangle]$
imposes a constraint on the two values associated with the types $\order{c}$ and
$\iorder{c}$; they must be ``synchronized'' by sharing the same $k$. In
general, a pointed type will be of the form
$\forall\overline{k}.[\mathbb{T},v]$ for some sequence of integers
$\overline{k}$ and some value $v$ in $\mathbb{T}$, which might of course refer
to the integers of $\overline{k}$ to enforce some synchronization among its
sub-values.  The resulting combinators are shown in Fig.~\ref{pifrac:comb}.
We omit the quantifier from the notation when it is over the empty sequence
integers.  We recall that, as all fractional types are inhabited (see remark in
Sec.~\ref{sec:symmetryg}), and thus there is no loss in generality in going to
pointed types.
